Estimating duration in the presence of misclassification

### 2024-03-08 introduction.tex
explain ch 7 contribution

\todo[inline]{Check what methodological claims I want to make about ch 7}
Finally, in \cref{E-SEIR}, I estimate the incidence of SARS-CoV-2 in England from only the CIS data.
This includes the development of a novel observation model to link the mechanistic transmission model to the data.
The observation model allows the inclusion of the long tail in the duration of positivity, without being computationally infeasible.

>>>>

Finally, in \cref{E-SEIR}, I estimate the transmission of SARS-CoV-2 in England using a mechanistic model, from only the CIS data.
This includes the development of a novel observation model to link the mechanistic transmission model to the data.
The observation model allows the inclusion of the skew in the duration of positivity, without being computationally infeasible.
